my title

### 2024-12-03 paper/paper.qmd
complete methodology and survey

>>>>

# Idealized Methodology

## Overview

The purpose of this study is to explore the key factors affecting the price of diamonds, including carat weight, color, clarity and cut. Through multi-wave data collection and strict data quality control, the goal of this study is to build an accurate forecasting model and provide a deep understanding of market trends. The research method combines extensive sample recruitment, diversified data collection techniques and statistical modeling tools to provide reliable basis for quantitative analysis and qualitative interpretation.

## SamplingApproach

In this study, stratified random sampling method is used to ensure that the samples are representative enough.

-   Stratification criteria include geographical area, income level and purchasing preference.
-   The sample size is set to 3000 to meet the confidence level of 95% and the error range of 3%.
-   Data sources include diamond retailers, auction platforms and online consumer surveys.

## Recruitment

Participants are recruited through the following channels:

-   Cooperate with major jewelry retailers and market research institutions to obtain target group information through sales data.
-   Put targeted advertisements on social media and email platforms to attract potential participants to fill in online surveys.
-   Provide small cash rewards (such as $10 gift cards) or lucky draw opportunities to increase participation rate and reduce bias.

All participants need to sign an electronic informed consent form to ensure that data collection conforms to ethical norms.

## Data Collection and Survey Design

Data is collected through various channels to ensure wide coverage and data quality:

-   The online survey platform is used to collect consumers' purchasing behavior, preferences and socio-economic background data.
-   Combined with the actual market data (such as transaction records), the questionnaire results are verified.

The questionnaire design includes:
-   Closed-form questions (multiple choice, Likert scale) to evaluate consumer preferences.
-   Open-ended questions gain insight into the factors affecting prices.
The questionnaire was optimized by small-scale pretest, focusing on reducing the ambiguity of questions and the fatigue of respondents

## Data Validation and Quality Control

-   In the data cleaning stage, incomplete and contradictory questionnaire responses were eliminated, and duplicate records were eliminated.
-   Using outlier detection technology to identify and deal with possible problem data points.
-   Re-verify key data points by tracking some interviewees to ensure the consistency and reliability of the answers.

## Multi-Wave Data Collection and Aggregation

In order to study market trends and price changes, data collection is divided into three waves, each with a quarterly interval:

-   Wave 1: Obtain the data of consumers' price sensitivity and buying habits in peak sales season (such as festivals).
-   Wave 2: Investigate the off-season market demand and price elasticity.
-   Wave 3: verify the stability of the model, focusing on the analysis of the changing trend of bulk diamond buying behavior.

The data are aggregated after standardization among waves to ensure the consistency of time series analysis.

## Budget Allocation

The total budget is estimated at $75,000.The allocation of funds is as follows:

-   Sample recruitment and incentives (35%): including gift cards and advertising expenses.
-   Data collection and processing (25%): Covers the cost of online platform and cleaning tools.
-   Questionnaire design and pilot test (15%): design optimization and forecast trial expenditure.
-   Data analysis and report writing (15%): including software use and labor costs.
-   Quality control (10%): data verification and tracking verification costs.

# Idealized Survey

The idealized survey questionnaire can be accessed via the following link:

https://docs.google.com/forms/d/e/1FAIpQLSe9YMFwC4RHHg36c1VY8yA-cZpdrN32yZfeCMJf_jD3qweOQg/viewform?usp=sf_link

## Survey Questions

**Demographic Questions**:

1. What is your age? (open)

2. What's your gender? (M/F/Other)

3. What is your main source of income? (Fixed income/freelance/other)

**Behavioral Patterns**:

4. How often did you buy diamonds in the past year? (Never/once /2-3 times/more than 3 times)

5. Where do you prefer to buy diamonds? (Holiday gifts/engagement or marriage/investment/other)

**Perceptions and Attitudes**:

6. Which of the following do you think has the greatest influence on the price of diamonds? (carat/color/clarity/cut/brand)

7. How do you evaluate the importance of the following diamond characteristics: carat size, color, clarity, cut? (1- very unimportant, 5- very important)

**Outcome Measures**:

8. Assuming the same price, which of the following diamonds would you prefer to buy? (Grade D color /IF clarity /1.5 carats)

9. Please rate your satisfaction with the last diamond purchase (1- very dissatisfied, 5- very satisfied).

**Open-Ended Questions**
:
10. What do you think are the main challenges in the diamond market at present?

11. Please describe the main reason why you choose a diamond.
